---
title: "DOM analysis"
subtitle: "EEM peak picking, absorbance slope parameters"
date: "`r format(Sys.time(), '%B %e %Y')`"
author: "WCL"
knit: (function(inputFile, encoding) {
      output_dir = '~/output/';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(output_dir,paste0('DOM_EEM_analysis_report_',format(Sys.time(), "%Y%m%d_%H%M%S"),'.htm')))
                        })
output: 
  html_document:
    df_print: paged
    number_sections: yes
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---
This report was created using the R package staRdom version `r packageVersion("staRdom")`, (`r packageDescription("staRdom")$Author`, `r unlist(strsplit(packageDescription("staRdom")$Date,"-"))[1]`). The used template EEM_simple_analysis.Rmd was taken from staRdom 0.1.12.

# Parameter specification
## Input parameters
```{r, include=FALSE}
###################################################
#### Version 1.0.13 of EEM_simple_analysis.Rmd ####
###################################################
# Please use the same versions of staRdom and EEM_simple_analysis.Rmd
# In general, there was no problem so far mixing the versions, but some
# changes and maybe future changes might cause problems if you use
# different versions!
#
##############################
#### load staRdom package ####
##############################
#
library(dplyr)
library(tidyr)
library(staRdom)
#
####################################
#### Documentation of this file ####
####################################
# This file comes with an extensive documentation.
# You can find it as a vignette.
# 
#################################
#### Define output directory ####
#################################
#     .      
#   .:;:.     Please look at the top of the file!
# .:;;;;;:.   If you want to write a protocol with knitr,
#   ;;;;;     you need to specify the output directory aobve (line 7):
#   ;;;;;     output_dir = 'C:/some_folder/output/';
#   ;;;;;
#
# Set the directory where all output files are put in.
# The directory is automatically created if it does not exist.
# Folder delimiters can be / or \\. \ , as it is usually used in Windows, will not work!
output_dir = "~/output/" # e.g. output_dir = "C:/some_folder/output/"

```

```{r}
#############################
#### Define data sources ####
#############################
# Please avoid "-" (minus) and space in file and column names and numbers at the beginning of file and column names!

#### Directory containing EEM data ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Set the directory with your sample files. Please see eem_read() help for details on file formats.
# Sub folders are read in and are considered different sample sets.
# Import is done with eem.read() (package eemR), please see details there.
# The template refers to data coming with the package. Please use your data
# by setting the path to your files!
sample_dir = system.file("extdata/EEMs", package = "staRdom") # e.g. sample_dir = "C:/some_folder/input/fluor/", system.file() accesses the example data coming with the package!
# Set the used instrument:
# Cary Eclipse: "cary" 
# Aqualog: "aqualog"
# Shimadzu: "shimadzu"
# Fluoromax-4: "fluoromax4"
# And furthermore, without hyphens:
# generic csv, excitation column-wise: eem_csv
# generic csv, emission column-wise: eem_csv2
# Hitachi F-7000: eem_hitachi
fluorometer = eem_csv

#### Absorbance data ####
#~~~~~~~~~~~~~~~~~~~~~~~#
# Absorbance data is read from *.TXT or *.CSV files.
# Either a directory containing one or more files can be named or a single file containing all samples.
# Absorbance data is used for inner-filter-effect correction and calculation of the slope parameters.
# Those steps can be skipped but keep in mind it is important for a profound analysis!
#
# path of adsorbance data as directory or single file, sub folders are not read:
absorbance_dir = system.file("extdata/absorbance",package = "staRdom") # e.g. absorbance_dir = "C:/some_folder/input/absorbance/", system.file() accesses the exmaple data coming with the package!

# Path length of absorbance measurement in cm that was used in absorbance measurement.
# If it is set to "meta" data from the metadata table is used (details see below).
absorbance_path = 1 # e.g. absorbance_path = 5

#### Meta data ####
#~~~~~~~~~~~~~~~~~#
# Adding a table with meta data is OPTIONAL!
# The table can contain dilution factors, path lengths of
# the photometer and raman areas and is intended
# for cases where different values should be used for different
# samples. Each column can be used optionally.

# read table with metadata as *.TXT or *.CSV
# either a path or FALSE if no metadata file is used.
metadata = system.file("extdata/metatable_dreem.csv",package = "staRdom") # e.g. metadata = "C:/some_folder/input/metatable.csv", system.file() accesses the exmaple data coming with the package!

#### Meta data: names of columns ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# column with sample names
col_samples = "sample"

# if you want to use dilution factors (e.g. 10 if 1 part sample and 9 parts solvent) from the meta data table, state the name 
# of the column containing the dilution data and set dilution = "meta" (below)
col_dilution = "dilution"

# if you want to use the cuvette length (in cm) for the absorbance from the meta data table,
# state the name of the column containing the cuvette lengths and set absorbance_path = "meta" (below)
col_cuv_len = "cuv_len"

# if you want to use the raman area (under the curve) data from the meta data table, state the name 
# of the column containing the raman areas and set raman_normalisation = "meta" (below)
col_raman_area = "raman"

#### Spectral correction of EEMs ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Some instruments, but not all need a spectral correction to compensate
# for specific deviations in the measurements. A vector for emission and
# excitation is used each. EEMs are cut to match the wavelength range of
# the vectors if used. Please provide paths to csv tables containing
# wavelengths in the first column and correction values in the second. If
# you do not want spectral correction to be done, setting these two input
# files it not necessary. 
# Emission correction vector
Emcor <- system.file("extdata/CorrectionFiles/mcorrs_4nm.csv",package="staRdom") # e.g. "C:\folder\emcor.csv", FALSE
# Excitation correction vector
Excor <- system.file("extdata/CorrectionFiles/xc06se06n.csv",package="staRdom")
```
## Output parameters
```{r}
###############################
#### Define desired output ####
###############################

#### Table output ####
#~~~~~~~~~~~~~~~~~~~~#
# Write a table with peaks and slope parameters.
# Written as xls or, in case of missing java environment or the package xlsx as csv.
output_xls = TRUE # e.g. TRUE

# In case of a csv export you can define the separator and the decimal point here.
out_sep_dec = c("\t",".") # e.g. out_sep_dec = c("\t",".")

#### Plot settings PNG ####
#~~~~~~~~~~~~~~~~~~~~~~~~~#
# State whether you want pngs of the single EEM spectra written in your output directory
output_single_png = FALSE # e.g. TRUE

## State whether you want pngs of multiple EEM spectra written in your output directory
output_overview_png = FALSE # e.g. TRUE

## number of EEM spectra plottet in each overview image
overview_number = 6 # e.g. 6

# The scaling of the different sample plots can be chosen.
# Either all samples are coloured according to the range of the
# complete sample set (TRUE) or each plot is scaled separately (FALSE).
scale_col = FALSE # e.g. TRUE

# Add contours to yout plots?
contours = FALSE

#### Plot settings report ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# This block defines which plots are included in the report.
#
# Add plots with several EEM samples per plot. 
# The number per plot is defined by overview_number above.
overview = TRUE # e.g. TRUE

# State whether you want plots from single EEM spectra in the report.
single_plots = FALSE # e.g. TRUE

#### Save data for further (R) analysis ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# File name where data is stored in RData format in the output directory.
# Set to FALSE if you dont want your eem data saved.
# Date, time and file extension is added automatically so you do not overwrite previous saved data.
data_file = "eem_data" # e.g. "eem_data"" or FALSE

# Desired name for the variable containing the eem data.
eem_name = "eem_list"

```
## Correction parameters

```{r}
#########################
#### Data correction ####
#########################
#
#### Normalising absorbance data to baseline ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Absorbance data can be corrected by subtracting a baseline value from each sample.
# In high wavelength ranges (default 680-700 nm), the absorbance is assumed to be 0.
# The average value of that range (or any other range) is subtracted from the whole spectrum.
# abs_norm can be set TRUE to use the default range, you can specify the desired range by a vector of length 2 and you can set it FALSE to skip this correction.
abs_norm = TRUE # e.g. TRUE, c(700,800)

#### Correction of diluted samples ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Set a dilution factor if your sample was diluted.
# All samples are multiplied with this factor.
# Please use a meta table (above) if your dilutions are differing
# 1 for no dilution, 10 for dilution 1:10 (1 part sample and 9
# parts milliq), "meta" for data from meta table
dilution = "meta" # e.g. 1

# In case of diluted samples, two absorbance measurements of the
# same sample in different dilutions might be present. If this is
# the case, EEMs are renamed to the undiluted sample, absorbance
# data might be multiplied by the dilution factor if it is only
# presentas diluted sample. This can be done automatically. In the
# final protocol a table shows, what has been done to the samples.
# Please check this table and see, if the output is what you
# wanted it to be!
dil_sample_name_correction = FALSE

#### Spectral correction of EEMs ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Some instruments, but not all need a spectral correction to compensate
# for specific deviations in the measurements. Please sepecify, if you want
# spectral correection to be done.
spectral_cor = TRUE # e.g. TRUE, set to FALSE, if your instrument already provided EEMs with spectral correction
  
#### Cut data to certain range ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Set a vector with range of wavelengths to be plotted and saved.
# Peak picking is done before range reduction.
# Emission wavelength:
em_range = c(0,Inf) # e.g. c(300,500), c(0,Inf) to use everything

# Excitation wavelength:
ex_range = c(0,Inf) # e.g. c(300,500), c(0,Inf) to use everything

# Cut all samples to fit largest range available in all samples
cut_range_to_smallest = FALSE # e.g. FALSE

#### Blank correction ####
#~~~~~~~~~~~~~~~~~~~~~~~~#
# A blank sample is subtracted from each sample. Blank samples have to be
# in the same (sub)folder as the according EEM samples. So different blanks are used
# for different subsets. The file names of the blanks have to contain nano, 
# miliq, milliq, mq or blank (cases are ignored). Other samples must not 
# contain these words in their names respectively!
blank_correction = FALSE # e.g. FALSE

#### Inner filter effect correction ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Inner filter effects are corrected. Absorbance data is needed. File or column designations
# of the absorbance data have to resamble file names of the EEM data.
ife_correction = TRUE # e.g. FALSE

#### Remove scattering and interpolate missing data ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Scattering is removed from the EEM spectra.
remove_scatter <- c(TRUE, TRUE, TRUE, TRUE) # logical values, ordered by raman1,raman2,rayleigh1,rayleigh2

# Set the width of removed scatter slot (usually 10 to 20).
# If you can still see traces of scattering after interpolation,
# this value should be increased. You can specify a vector containing
# separate widths for each scatter c(15,16,16,14), ordered by raman1,raman2,rayleigh1,rayleigh2.
remove_scatter_width = c(15,20,15,18) # e.g. 15 or c(15,15,15,15)

# state whether removed scattering should be interpolated
interpolation <- TRUE # e.g. TRUE

#### Raman normailsation ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# State whether a Raman normalisation should be performed
# Either "blank" if a blank is present in each (sub)folder of the EEM data.
# Blank samples have to be in the same (sub)folder as the EEM samples. So 
# different blanks are used for different subsets. The file names of the 
# blanks have to contain nano, miliq, milliq, mq or blank (cases are ignored).
# Other samples must not contain these words in their names respectively!
# Normalisation is then calculated with this blank, the raman area as a number
# or "meta" if the raman areas should be taken from the meta data table.
raman_normalisation = "blank" # e.g. "blank", FALSE, 160, "meta"


#### Smooth data for peak picking ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Moving window size in nm for smoothing data along excitation wavelengths.
# Data must be interpolated if you want to use smoothing.
# This is used for peak picking but not saved.
smooth = 4 # e.g. FALSE, 4
```
```{r, message=FALSE, warning=TRUE, include=FALSE}
#############################################
#                                           #
#       THERE ARE NO SETTINGS BELOW.        #
#  YOU CAN KLICK "KNIT" AT THE MENU BAR.    #
#  In case of errors, chunk-wise execution  #
#     of the code can reveal problems!      #
#                                           #
#     Please read the help of the used      #
#        functions if you encounter         #
#               any problems:               #
#   Press F1 while cursor in function or    #
#   type help(function) in command line!    #
#                                           #
#             Please read the               #
#        error messages carefully!          #
#    Naming of the input files and table    #
#     column and row names is crucial!      #
#                                           #
#############################################
```

```{r, message=FALSE, warning=TRUE, include=FALSE}
###################
#### Read data ####
###################

#### Read EEM data ####
#~~~~~~~~~~~~~~~~~~~~~#
# recursive = TRUE means, that subdirectories are included in reading
eem_list <- eem_read(sample_dir, recursive = TRUE, import_function = fluorometer)

#### Alter names of EEM samples ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# In this case, "(FD3)" is replaced by nothing from sample name.
# It is a Hitachi related thing
eem_list <- eem_list %>% eem_name_replace(c("\\(FD3\\)"),c(""))

#### Read table with meta data ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# There is an additional step to automatically reread the table with comma decimal separator if dot did not work.
if(metadata != FALSE){
  meta <- data.table::fread(file = metadata, header = TRUE)
  if(!all(sapply(meta,is.numeric)[-which(colnames(meta) == col_samples)])) meta <- data.table::fread(file = metadata, header = TRUE,dec=",")
  meta <- meta %>% mutate_at(vars(one_of(col_samples)),make.names) %>%
    tibble::column_to_rownames(var=col_samples)
}

#### Read absorbance data ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(absorbance_dir != FALSE){
  abs_data <- absorbance_read(absorbance_dir, verbose = FALSE)
  if(abs_norm != FALSE){
    if(abs_norm == TRUE) abs_norm <- c(680, 700)
    abs_data <- abs_blcor(abs_data,abs_norm)
  }
}

```

```{r echo=FALSE, message=TRUE, warning=TRUE}
####################
#### Data check ####
####################
# the data is checked for several often occuring problems. Most of them are related to how you organised your data.
# if the script stops here please have a look at the error messages and correct your data.
eem_checkdata(eem_list,abs_data,metadata = meta,metacolumns = c(col_dilution, col_cuv_len, col_raman_area), error = FALSE)
```

```{r message=FALSE, warning=TRUE, include=FALSE}
#########################
#### Data correction ####
#########################
#
#### Spectral correction ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(spectral_cor){
  Excor <- data.table::fread(Excor)
  Emcor <- data.table::fread(Emcor)
# adjust range of EEMs to cover correction vectors
  eem_list <- eem_range(eem_list,ex = range(Excor[,1]), em = range(Emcor[,1]))

  eem_list <- eem_spectral_cor(eem_list,Excor,Emcor)
}

#### Blank substraction ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~#
# substract blank, blank needed for that, can remove scattering and other noise partly
if(blank_correction) eem_list <- eem_list %>% eem_remove_blank()

#### Inner filter effects correction ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(absorbance_dir != FALSE){
  if(absorbance_path == "meta") cuvl <- meta[col_cuv_len] else cuvl <- absorbance_path
  if(ife_correction) eem_list <- eem_list %>% eem_ife_correction(abs_data,cuvl)
}

#### Raman normalisation ####
#~~~~~~~~~~~~~~~~~~~~~~~~~#
if(raman_normalisation != FALSE){
  if(raman_normalisation == "meta") ram_data <- meta[col_raman_area] else ram_data <- raman_normalisation
  eem_list <- eem_list %>% eem_raman_normalisation2(ram_data)
}

#### Remove blank samples from sample list ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Blanks used for correction are not needed anymore from this step
eem_list <- eem_list %>%
  eem_extract(c("nano", "miliq", "milliq", "mq", "blank"),ignore_case = TRUE)

abs_data <- abs_data %>%
  select(-matches("nano|miliq|milliq|mq|blank",ignore.case=TRUE))

#### Remove scattering ####
#~~~~~~~~~~~~~~~~~~~~~~~#
# raman and rayleigh scattering
eem_list <- eem_rem_scat(eem_list,remove_scatter,remove_scatter_width)

#### Interpolate scattering ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Removing scattering left NAs. They will be interpolated.
if(interpolation) eem_list <- eem_list %>% eem_interp(type = TRUE, extend = FALSE)

#### Correct dilution ####
#~~~~~~~~~~~~~~~~~~~~~~#
# Samples are multiplyed with dilution factor
if(dilution == "meta") dil_data <- meta[col_dilution] else dil_data <- dilution
eem_list <- eem_list %>% eem_dilution(dil_data)

# Sample names are corrected to put similar samples together and
# correct absorbance data according to dilution
if(dil_sample_name_correction){
  # find out what is done
  dc <- eem_dilcorr(eem_list, abs_data, dilution = dil_data, auto=TRUE)
  # apply to absorbance data
  abs_data <- eem_absdil(abs_data, cor_data = dc)
  # apply to EEM data
  eem_list <- eem_eemdil(eem_list, cor_data = dc)
}

#### Smooth data for peak picking only ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(smooth != FALSE & interpolation) eem4peaks <- eem_list %>% eem_smooth(n=smooth) else eem4peaks <- eem_list

####################################################
#### Peak picking and slope parameter calculation ####
####################################################
#
#### Peak picking ####
#~~~~~~~~~~~~~~~~~~#
indices_peaks <- eem4peaks %>% eem_biological_index() %>%
  full_join(eem4peaks %>% eem_coble_peaks(), by="sample")  %>%
  full_join(eem4peaks %>% eem_fluorescence_index(), by="sample") %>%
  full_join(eem4peaks %>% eem_humification_index(scale=TRUE), by="sample") 

#### Slope parameter calculation ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(absorbance_dir != FALSE){
  indices_peaks <- indices_peaks %>%
    full_join(abs_parms(abs_data,cuvl,p=TRUE), by="sample")
}

################################
#### Reduction of wavelengths ####
################################
#
#### Reduce to defined range ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
eem_list <- eem_list %>% eem_range(ex=ex_range,em=em_range)

#### Reduce to largest range found in all samples ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(cut_range_to_smallest) eem_list <- eem_list %>% eem_red2smallest()

```

```{r, message=FALSE, warning=TRUE, include=FALSE}
##################################
#### Write out data and results ####
##################################
#
#### Create output directory if neccessary ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
if(!dir.exists(file.path(output_dir))) dir.create(file.path(output_dir),recursive=TRUE)

#### Write out table with results ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Write picked peaks and absorbance slope parameters to table.
# First try to write XLS, if not possible CSV.
if(output_xls){
  xls <- try(xlsx::write.xlsx(indices_peaks, file=paste0(output_dir,"picked_peaks_",format(Sys.time(), "%Y%m%d_%H%M%S"),".xlsx"), sheetName = paste0("picked_peaks_",format(Sys.time(), "%Y%m%d_%H%M%S")),col.names=TRUE, row.names=FALSE),silent=TRUE)
  
  if(class(xls) == "try-error"){
    write.table(indices_peaks, file=paste0(output_dir,"picked_peaks_",format(Sys.time(), "%Y%m%d_%H%M%S"),".csv"), dec = out_sep_dec[2],col.names=TRUE,row.names=FALSE,sep=out_sep_dec[1],quote=TRUE,fileEncoding="UTF-8")
  }
  
}

#### Write RData files with corrected EEM data and absorbance ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
# Rename to variable name stated above and saved to file stated
# above with current date and time added.
assign(eem_name,eem_list)

if(data_file != FALSE){
  save(list=c(eem_name,"abs_data","meta"),file = paste0(output_dir,data_file,"_",format(Sys.time(), "%Y%m%d_%H%M%S"),".RData"))
}
```
# Sample overview

```{r, echo=FALSE, message=FALSE, warning=TRUE}
#####################################################
#### Summary of your EEM data as table in report ####
#####################################################

if(class(try(library(kableExtra),silent=TRUE)) != "try-error" & class(try(library(knitr),silent=TRUE)) != "try-error") {
  eem_list %>%
    summary() %>%
    kable(format = "html", booktabs = T) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) #%>%
  #kable_styling(font_size = 5) %>%
  #row_spec(0, angle = -45) #%>%
  #landscape()
} else {
  eem_list %>%
    summary()
}
if (exists("dc")){

asis_output("# Dilution correction")
  
###################################################################
#### Summary of corrections that were done for dilution issues ####
###################################################################
  
  if(class(try(library(kableExtra),silent=TRUE)) != "try-error" & class(try(library(knitr),silent=TRUE)) != "try-error") {
    dc %>%
      kable(format = "html", booktabs = T) %>%
      kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
  } else {
    dc
  }
}
```

# Results from peak picking
```{r, echo=FALSE, message=FALSE, warning=TRUE}
#########################################################################
#### Results from peak picking and slope parameters as table in report ####
#########################################################################

if(class(try(library(kableExtra),silent=TRUE)) != "try-error" & class(try(library(knitr),silent=TRUE)) != "try-error") {
  kable(indices_peaks %>% mutate_if(is.numeric,prettyNum,digits = 2,format="fg"),format = "html", booktabs = T) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) #%>%
  #kable_styling(font_size = 5) %>%
  #row_spec(0, angle = 45) #%>%
  #landscape()
} else {
  indices_peaks %>%
    mutate_if(is.numeric,prettyNum,digits = 2,format="fg")
}
```

# Plots of EEM spectra
```{r, echo=FALSE, message=FALSE, warning=TRUE}
######################
#### Overview plots ####
######################
# 
# Overview plots are generated and printed into report

if(overview | output_overview_png) {
  ov_plots <- eem_list %>%
    eem_overview_plot(spp = overview_number, contours = contours)
}

if(overview){
  lapply(ov_plots,print) %>%
    invisible()
}

```

```{r, echo=FALSE, message=FALSE, warning=TRUE}
####################
#### Single plots ####
####################
# 
# Single plots are generated and printed into report

if(scale_col) fill_max <- eem_list %>% eem_scale_ext() %>% .[2] else fill_max <- FALSE

if(output_single_png | single_plots){
  sing_plots <- lapply(eem_list, ggeem, fill_max = fill_max, contours = contours)
}

if(single_plots){
  lapply(sing_plots,print) %>%
    invisible()
}
```

```{r, message=TRUE, warning=TRUE, include=FALSE, paged.print=FALSE}
#################
#### PNG plots ####
#################
# 
# PNGs of plots are written to output directory

if(output_overview_png){
  lapply(ov_plots, function(pl){
    png(paste0(output_dir,"/EEM_overview_",format(Sys.time(), "%Y%m%d_%H%M%S"),'.png',sep=""),width=1000,height=1000,units = "px", pointsize = 25)
    plotp <- pl + theme(text = element_text(size=35))
    print(plotp)
    dev.off()
  })
}

if(output_single_png){
  lapply(1:length(sing_plots), function(n){
    pl <- sing_plots[[n]]
    name <- eem_names(eem_list)[n]
    png(paste0(output_dir,"/EEM_single_",name,"_",format(Sys.time(), "%Y%m%d_%H%M%S"),'.png',sep=""),width=1000,height=1000,units = "px", pointsize = 25)
    plotp <- pl + theme(text = element_text(size=35))
    print(plotp)
    dev.off()
  })
}
```

